$N_{\text{eff}}$ priors

### 2015-05-25 Notes/N_eff_prior_paper.tex
change notes

@@

>>>>

\begin{itemize}
\item We are now using a simplistic lensing noise but I have lensing noise with the usual Hu Okamoto formula. Iterative Seljack not there yet.
\item We are varying $\tau ~ n_{s} ~ A_{s} ~ N_{\rm eff} ~ H_{0}$. The neutrino sector consists of one massive neutrino of $m_{\nu}=0.083$ eV, $\Omega_{\nu}h^{2}=0.0009$
\item Next TODO: Check for bugs and errors code in its early stages. PCA? what prior is more important? Full MCMC should not be extremely hard with cosmosis.
\end{itemize}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{PS_with_noise.pdf}
\caption{CMB power spectrum for our fiducial cosmology together with the instrumental noise used in this work.}
\label{fig:cmb-cl-noise}
\end{center}
\end{figure}
